Artificial ecosystem selection reveals relationships between microbiome composition and ecosystem function

### 2022-04-27 Manuscript/manuscript.Rmd
update data availability statement

The 16S rRNA sequencing data generated during the current study are available in the NCBI Sequence Read Archive (SRA).

>>>>

The 16S rRNA sequencing data generated during the current study are available in the NCBI Sequence Read Archive (SRA) under BioProject accession number PRJNA832314, https://www.ncbi.nlm.nih.gov/sra/PRJNA832314. The metadata generated during the current study as well as the scripts to recreate the analysis are available on Github, https://github.com/amorris28/artificial_ecosystem_selection.
